---
title: "The female rivalry hypothesis - Sensitivity Analyses 2"
author: Scott Claessens
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
    toc: true
    number_sections: false
    toc_float: true
---

```{r warning=F, message=F}
library(tidyverse)
library(cowplot)
library(lme4)
library(lmerTest)
```

For further sensitivity analyses, we fixed the conditions of the agent-based model to those in Experiment 3, and manipulated one parameter at a time to see how sensitive our main result was to model variations.

# 1. Offspring investment

First, we manipulate the number of "offspring investment" units required to successfully have a child. Load in the data.

```{r echo=F, eval=F, warning=F, message=F}
# read data file
d <- read.csv("data/v6/rawData/OvModel_updatedForNetlogo6 Sensitivity Analysis 6 (Offspring Invest Max)-spreadsheet.csv", 
              header = FALSE, skip = 6)

# transform and clean
d <- 
  d %>%
  gather(key = key, value = value, 2:ncol(d)) %>% 
  spread(key = names(d)[1], value = "value") %>%
  transmute(Run       = as.numeric(`[run number]`),
            Sens      = as.numeric(offspring_invest_max_amount),
            Strategy  = factor(ifelse(grepl("1", `[initial & final values]`, fixed = TRUE), "Revealers", "Concealers")),
            key       = factor(ifelse(grepl("[cum_paternal_i]", `[initial & final values]`, fixed = TRUE), "PI", "RS")),
            value     = as.numeric(V1)) %>%
  arrange(Run, Strategy) %>%
  fill(Sens) %>%
  spread(key, value)

# save clean file
write.csv(file = "data/v6/cleanData/ovulationSensitivity2_OffspringInvest.csv", d, row.names = FALSE)
```

```{r}
d <-
  read.csv('data/v6/cleanData/ovulationSensitivity2_OffspringInvest.csv') %>%
  as_tibble() %>%
  mutate(Run      = factor(Run),
         Sens     = factor(Sens),
         Strategy = factor(Strategy))
```

There are 1800 rows (9 parameter values x 100 runs x 2 female strategies).

## 1.1. Analyses

We run mixed ANOVAs to determine (a) the main effect of the required offspring investment ('Sens'), (b) the main effect of Strategy, and (c) the interaction between these. Our first ANOVA includes lifetime reproductive success as the dependent variable.

```{r}
m1.1 <- aov(RS ~ Sens*Strategy + Error(Run/Strategy), data = d)

summary(m1.1)
```

```{r}
model.tables(m1.1, "means")
```

This analysis shows that, as the required offspring investment increases, the number of children decreases. Of course, this makes sense. But the interaction with Strategy implies that Concealers still have more children than Revealers.

Let's run the same model with paternal investment as the dependent variable.

```{r}
m1.2 <- aov(PI ~ Sens*Strategy + Error(Run/Strategy), data = d)

summary(m1.2)
```

```{r}
model.tables(m1.2, "means")
```

As the required offspring investment increases, the parental investment increases. Again, this makes sense. Our main result is robust to this sensitivity analysis.

## 1.2. Visualisation

We now visualise the interaction between required offspring investment and female strategy with two line graphs, one for each dependent variable. Again, the code for this plot is hidden (see the source .Rmd code for details).

```{r echo=F, warning=F, message=F, fig.height=4, fig.width=12}
d <-
  d %>%
  mutate(Sens = as.numeric(levels(Sens))[Sens])

RS_Summary <- 
  d %>%
  group_by(Sens, Strategy) %>%
  summarise(RS_mean = mean(RS),
            RS_se = sqrt(var(RS) / length(RS)))

p1.1 <- 
  ggplot(d, aes(x = Sens, y = RS, colour = Strategy)) +
    geom_point(aes(y = RS_mean), size = 1, 
               data = RS_Summary, position = position_dodge(width = 1.5), 
               show.legend = FALSE) + 
    geom_errorbar(aes(y = RS_mean, ymin = RS_mean - RS_se, ymax = RS_mean + RS_se), 
                  width = 4, position = position_dodge(width = 1.5), data = RS_Summary) +
    geom_line(aes(y = RS_mean), position = position_dodge(width = 1.5), data = RS_Summary) +
    scale_colour_manual(values=c("#ffd3b4", "#6691b1")) +
    xlab("Required offspring investment (units)") +
    ylab("Reproductive success\n(number of children)") +
    ylim(c(0,12)) +
    theme_bw() +
    theme(text = element_text(size = 10),
          panel.grid = element_blank()) +
    guides(colour = FALSE)
    

PI_Summary <- 
  d %>%
  group_by(Sens, Strategy) %>%
  summarize(PI_mean = mean(PI),
            PI_se = sqrt(var(PI) / length(PI)))

p1.2 <- 
  ggplot(d, aes(x = Sens, y = PI, colour = Strategy)) +
    geom_point(aes(y = PI_mean), size = 1, 
               data = PI_Summary, position = position_dodge(width = 1.5), show.legend = FALSE) + 
    geom_errorbar(aes(y = PI_mean, ymin = PI_mean - PI_se, ymax = PI_mean + PI_se), 
                  width = 4, position = position_dodge(width = 1.5), data = PI_Summary) +
    geom_line(aes(y = PI_mean), position = position_dodge(width = 1.5), data = PI_Summary) +
    scale_colour_manual(values=c("#ffd3b4", "#6691b1")) +
    xlab("Required offspring investment (units)") +
    ylab("Paternal investment\n(units)") +
    ylim(c(0,16000)) +
    theme_bw() +
    theme(text = element_text(size = 10),
          panel.grid = element_blank())
    

plot_grid(p1.1, NULL, p1.2, labels = c('a', '', 'b'), nrow = 1, align = 'h',
          rel_widths = c(0.7375, 0.05, 1))

# cleanup
rm(PI_Summary, RS_Summary)
```

# 2. Population size

Next, we manipulate the population size. There are always 50% females and 50% males. Also, the females are always 50% Concealers and 50% Revealers. So a population size of 100 would have 50 males, 25 Concealer females, and 25 Revealer females. Load in the data.

```{r echo=F, eval=F, warning=F, message=F}
# read data file
d <- read.csv("data/v6/rawData/OvModel_updatedForNetlogo6 Sensitivity Analysis 7 (Population Size)-spreadsheet.csv", 
              header = FALSE, skip = 6)

# transform and clean
d <- 
  d %>%
  gather(key = key, value = value, 2:ncol(d)) %>% 
  spread(key = names(d)[1], value = "value") %>%
  filter(`[steps]` == "10000") %>%
  transmute(Run       = as.numeric(`[run number]`),
            Sens      = as.numeric(AcSig_num) + as.numeric(FertConceal_num) + as.numeric(num_males),
            Strategy  = factor(ifelse(grepl("1", `[initial & final values]`, fixed = TRUE), "Revealers", "Concealers")),
            key       = factor(ifelse(grepl("[cum_paternal_i]", `[initial & final values]`, fixed = TRUE), "PI", "RS")),
            value     = as.numeric(V1)) %>%
  arrange(Run, Strategy) %>%
  fill(Sens) %>%
  spread(key, value)

# save clean file
write.csv(file = "data/v6/cleanData/ovulationSensitivity2_OffspringInvest.csv", d, row.names = FALSE)
```

```{r}
d <-
  read.csv('data/v6/cleanData/ovulationSensitivity2_OffspringInvest.csv') %>%
  as_tibble() %>%
  mutate(Run      = factor(Run),
         Sens     = factor(Sens),
         Strategy = factor(Strategy))
```

There are 1200 rows (6 population sizes x 100 runs x 2 female strategies).

## 2.1. Analyses

We run mixed ANOVAs to determine (a) the main effect of population size, (b) the main effect of Strategy, and (c) the interaction between these. Our first ANOVA includes lifetime reproductive success as the dependent variable.

```{r}
m2.1 <- aov(RS ~ Sens*Strategy + Error(Run/Strategy), data = d)

summary(m2.1)
```

```{r}
model.tables(m2.1, "means")
```

This analysis shows that, as population sizes increase, the number of children increases. The interaction with Strategy implies that Concealers still have more children than Revealers.

Let's run the same model with paternal investment as the dependent variable.

```{r}
m2.2 <- aov(PI ~ Sens*Strategy + Error(Run/Strategy), data = d)

summary(m2.2)
```

```{r}
model.tables(m2.2, "means")
```

## 2.2. Visualisation

We now visualise the interaction between population size and female strategy with two line graphs, one for each dependent variable. Again, the code for this plot is hidden (see the source .Rmd code for details).

```{r echo=F, warning=F, message=F, fig.height=4, fig.width=12}
d <-
  d %>%
  mutate(Sens = as.numeric(levels(Sens))[Sens])

RS_Summary <- 
  d %>%
  group_by(Sens, Strategy) %>%
  summarise(RS_mean = mean(RS),
            RS_se = sqrt(var(RS) / length(RS)))

p2.1 <- 
  ggplot(d, aes(x = Sens, y = RS, colour = Strategy)) +
    geom_point(aes(y = RS_mean), size = 1, 
               data = RS_Summary, position = position_dodge(width = 1.5), 
               show.legend = FALSE) + 
    geom_errorbar(aes(y = RS_mean, ymin = RS_mean - RS_se, ymax = RS_mean + RS_se), 
                  width = 4, position = position_dodge(width = 1.5), data = RS_Summary) +
    geom_line(aes(y = RS_mean), position = position_dodge(width = 1.5), data = RS_Summary) +
    scale_colour_manual(values=c("#ffd3b4", "#6691b1")) +
    xlab("Population size (number of individuals)") +
    ylab("Reproductive success\n(number of children)") +
    ylim(c(0,12)) +
    theme_bw() +
    theme(text = element_text(size = 10),
          panel.grid = element_blank()) +
    guides(colour = FALSE)
    

PI_Summary <- 
  d %>%
  group_by(Sens, Strategy) %>%
  summarize(PI_mean = mean(PI),
            PI_se = sqrt(var(PI) / length(PI)))

p2.2 <- 
  ggplot(d, aes(x = Sens, y = PI, colour = Strategy)) +
    geom_point(aes(y = PI_mean), size = 1, 
               data = PI_Summary, position = position_dodge(width = 1.5), show.legend = FALSE) + 
    geom_errorbar(aes(y = PI_mean, ymin = PI_mean - PI_se, ymax = PI_mean + PI_se), 
                  width = 4, position = position_dodge(width = 1.5), data = PI_Summary) +
    geom_line(aes(y = PI_mean), position = position_dodge(width = 1.5), data = PI_Summary) +
    scale_colour_manual(values=c("#ffd3b4", "#6691b1")) +
    xlab("Population size (number of individuals)") +
    ylab("Paternal investment\n(units)") +
    ylim(c(0,16000)) +
    theme_bw() +
    theme(text = element_text(size = 10),
          panel.grid = element_blank())
    

plot_grid(p2.1, NULL, p2.2, labels = c('a', '', 'b'), nrow = 1, align = 'h',
          rel_widths = c(0.7375, 0.05, 1))

# cleanup
rm(PI_Summary, RS_Summary)
```

# 3. Proportion of females (MF ratio)

Next, we manipulate the proportion of females in the population.

```{r echo=F, eval=F, warning=F, message=F}
# read data file
d <- read.csv("data/v6/rawData/OvModel_updatedForNetlogo6 Sensitivity Analysis 8 (M:F Ratio)-spreadsheet.csv", 
              header = FALSE, skip = 6)

# transform and clean
d <- 
  d %>%
  gather(key = key, value = value, 2:ncol(d)) %>% 
  spread(key = names(d)[1], value = "value") %>%
  filter(`[steps]` == "10000") %>%
  transmute(Run       = as.numeric(`[run number]`),
            Sens      = (as.numeric(FertConceal_num) + as.numeric(AcSig_num)) / 
              (as.numeric(AcSig_num) + as.numeric(FertConceal_num) + as.numeric(num_males)), # proportion
            Strategy  = factor(ifelse(grepl("1", `[initial & final values]`, fixed = TRUE), "Revealers", "Concealers")),
            key       = factor(ifelse(grepl("[cum_paternal_i]", `[initial & final values]`, fixed = TRUE), "PI", "RS")),
            value     = ifelse(V1 == "<RuntimePrimitiveException>", 0, as.numeric(V1))) %>%
  arrange(Run, Strategy) %>%
  fill(Sens) %>%
  spread(key, value)

# save clean file
write.csv(file = "data/v6/cleanData/ovulationSensitivity2_MFRatio.csv", d, row.names = FALSE)
```

```{r}
d <-
  read.csv('data/v6/cleanData/ovulationSensitivity2_MFRatio.csv') %>%
  as_tibble() %>%
  mutate(Run      = factor(Run),
         Sens     = factor(Sens),
         Strategy = factor(Strategy))
```

There are 1000 rows (5 MF ratios x 100 runs x 2 female strategies).

## 3.1. Analyses

We run mixed ANOVAs to determine (a) the main effect of MF ratio, (b) the main effect of Strategy, and (c) the interaction between these. Our first ANOVA includes lifetime reproductive success as the dependent variable.

```{r}
m3.1 <- aov(RS ~ Sens*Strategy + Error(Run/Strategy), data = d)

summary(m3.1)
```

```{r}
model.tables(m3.1, "means")
```

There's a main effect of proportion of females. 0% and 100% females produce no children, while proportions in between do. 50:50 ratio is the sweet spot. But the main effect of Strategy and interaction effect indicate that Concealers have more children than Revealers.

Let's run the same model with paternal investment as the dependent variable.

```{r}
m3.2 <- aov(PI ~ Sens*Strategy + Error(Run/Strategy), data = d)

summary(m3.2)
```

```{r}
model.tables(m3.2, "means")
```

We get the same pattern.

## 3.2. Visualisation

We now visualise the interaction between MF ratio and female strategy with two line graphs, one for each dependent variable. Again, the code for this plot is hidden (see the source .Rmd code for details).

```{r echo=F, warning=F, message=F, fig.height=4, fig.width=12}
d <-
  d %>%
  mutate(Sens = as.numeric(levels(Sens))[Sens])

RS_Summary <- 
  d %>%
  group_by(Sens, Strategy) %>%
  summarise(RS_mean = mean(RS),
            RS_se = sqrt(var(RS) / length(RS)))

p3.1 <- 
  ggplot(d, aes(x = Sens, y = RS, colour = Strategy)) +
    geom_point(aes(y = RS_mean), size = 1, 
               data = RS_Summary, position = position_dodge(width = 0.05), 
               show.legend = FALSE) + 
    geom_errorbar(aes(y = RS_mean, ymin = RS_mean - RS_se, ymax = RS_mean + RS_se), 
                  width = 0.1, position = position_dodge(width = 0.05), data = RS_Summary) +
    geom_line(aes(y = RS_mean), position = position_dodge(width = 0.05), data = RS_Summary) +
    scale_colour_manual(values=c("#ffd3b4", "#6691b1")) +
    xlab("Proportion of females in population") +
    ylab("Reproductive success\n(number of children)") +
    ylim(c(0,12)) +
    theme_bw() +
    theme(text = element_text(size = 10),
          panel.grid = element_blank()) +
    guides(colour = FALSE)
    

PI_Summary <- 
  d %>%
  group_by(Sens, Strategy) %>%
  summarize(PI_mean = mean(PI),
            PI_se = sqrt(var(PI) / length(PI)))

p3.2 <- 
  ggplot(d, aes(x = Sens, y = PI, colour = Strategy)) +
    geom_point(aes(y = PI_mean), size = 1, 
               data = PI_Summary, position = position_dodge(width = 0.05), show.legend = FALSE) + 
    geom_errorbar(aes(y = PI_mean, ymin = PI_mean - PI_se, ymax = PI_mean + PI_se), 
                  width = 0.1, position = position_dodge(width = 0.05), data = PI_Summary) +
    geom_line(aes(y = PI_mean), position = position_dodge(width = 0.05), data = PI_Summary) +
    scale_colour_manual(values=c("#ffd3b4", "#6691b1")) +
    xlab("Proportion of females in population") +
    ylab("Paternal investment\n(units)") +
    ylim(c(0,16000)) +
    theme_bw() +
    theme(text = element_text(size = 10),
          panel.grid = element_blank())
    

plot_grid(p3.1, NULL, p3.2, labels = c('a', '', 'b'), nrow = 1, align = 'h',
          rel_widths = c(0.7375, 0.05, 1))

# cleanup
rm(PI_Summary, RS_Summary)
```

# 4. Proportion of Concealers (Concealer:Revealer ratio)

Next, we manipulate the proportion of Concealers among females.

```{r echo=F, eval=F, warning=F, message=F}
# read data file
d <- read.csv("data/v6/rawData/OvModel_updatedForNetlogo6 Sensitivity Analysis 9 (Concealer:Revealer Ratio)-spreadsheet.csv", 
              header = FALSE, skip = 6)

# transform and clean
d <- 
  d %>%
  gather(key = key, value = value, 2:ncol(d)) %>% 
  spread(key = names(d)[1], value = "value") %>%
  filter(`[steps]` == "10000") %>%
  transmute(Run       = as.numeric(`[run number]`),
            Sens      = as.numeric(FertConceal_num) / (as.numeric(AcSig_num) + as.numeric(FertConceal_num)), # proportion
            Strategy  = factor(ifelse(grepl("1", `[initial & final values]`, fixed = TRUE), "Revealers", "Concealers")),
            key       = factor(ifelse(grepl("[cum_paternal_i]", `[initial & final values]`, fixed = TRUE), "PI", "RS")),
            value     = ifelse(V1 == "<RuntimePrimitiveException>", 0, as.numeric(V1))) %>%
  arrange(Run, Strategy) %>%
  fill(Sens) %>%
  spread(key, value)

# save clean file
write.csv(file = "data/v6/cleanData/ovulationSensitivity2_ConcRevRatio.csv", d, row.names = FALSE)
```

```{r}
d <-
  read.csv('data/v6/cleanData/ovulationSensitivity2_ConcRevRatio.csv') %>%
  as_tibble() %>%
  mutate(Run       = factor(Run),
         Sens      = factor(Sens),
         Strategy  = factor(Strategy))
```

There are 1200 rows (7 ratios x 100 runs x 2 female strategies).

## 4.1. Analyses

We run mixed ANOVAs to determine (a) the main effect of Concealer:Revealer ratio, (b) the main effect of Strategy, and (c) the interaction between these. Our first ANOVA includes lifetime reproductive success as the dependent variable.

```{r}
m4.1 <- aov(RS ~ Sens*Strategy + Error(Run/Strategy), data = d)

summary(m4.1)
```

```{r}
model.tables(m4.1, "means")
```

There's a main effect of proportion of Concealers. The main effect of Strategy and interaction effect indicate that Concealers have more children than Revealers.

Let's run the same model with paternal investment as the dependent variable.

```{r}
m4.2 <- aov(PI ~ Sens*Strategy + Error(Run/Strategy), data = d)

summary(m4.2)
```

```{r}
model.tables(m4.2, "means")
```

We get the same pattern.

## 4.2. Visualisation

We now visualise the interaction between Concealer:Revealer ratio and female strategy with two line graphs, one for each dependent variable. Again, the code for this plot is hidden (see the source .Rmd code for details).

```{r echo=F, warning=F, message=F, fig.height=4, fig.width=12}
d <-
  d %>%
  mutate(Sens = as.numeric(levels(Sens))[Sens])

RS_Summary <- 
  d %>%
  group_by(Sens, Strategy) %>%
  summarise(RS_mean = mean(RS),
            RS_se = sqrt(var(RS) / length(RS)))

p4.1 <- 
  ggplot(d, aes(x = Sens, y = RS, colour = Strategy)) +
    geom_point(aes(y = RS_mean), size = 1, 
               data = RS_Summary, position = position_dodge(width = 0.05), 
               show.legend = FALSE) + 
    geom_errorbar(aes(y = RS_mean, ymin = RS_mean - RS_se, ymax = RS_mean + RS_se), 
                  width = 0.1, position = position_dodge(width = 0.05), data = RS_Summary) +
    geom_line(aes(y = RS_mean), position = position_dodge(width = 0.05), data = RS_Summary) +
    scale_colour_manual(values=c("#ffd3b4", "#6691b1")) +
    xlab("Proportion of Concealers (within females)") +
    ylab("Reproductive success\n(number of children)") +
    ylim(c(0,12)) +
    theme_bw() +
    theme(text = element_text(size = 10),
          panel.grid = element_blank()) +
    guides(colour = FALSE)
    

PI_Summary <- 
  d %>%
  group_by(Sens, Strategy) %>%
  summarize(PI_mean = mean(PI),
            PI_se = sqrt(var(PI) / length(PI)))

p4.2 <- 
  ggplot(d, aes(x = Sens, y = PI, colour = Strategy)) +
    geom_point(aes(y = PI_mean), size = 1, 
               data = PI_Summary, position = position_dodge(width = 0.05), show.legend = FALSE) + 
    geom_errorbar(aes(y = PI_mean, ymin = PI_mean - PI_se, ymax = PI_mean + PI_se), 
                  width = 0.1, position = position_dodge(width = 0.05), data = PI_Summary) +
    geom_line(aes(y = PI_mean), position = position_dodge(width = 0.05), data = PI_Summary) +
    scale_colour_manual(values=c("#ffd3b4", "#6691b1")) +
    xlab("Proportion of Concealers (within females)") +
    ylab("Paternal investment\n(units)") +
    ylim(c(0,16000)) +
    theme_bw() +
    theme(text = element_text(size = 10),
          panel.grid = element_blank())
    

plot_grid(p4.1, NULL, p4.2, labels = c('a', '', 'b'), nrow = 1, align = 'h',
          rel_widths = c(0.7375, 0.05, 1))

# cleanup
rm(PI_Summary, RS_Summary)
```

# 5. Lattice size

Next, we manipulate the size of the world. It's always a square (height == width).

```{r echo=F, eval=F, warning=F, message=F}
# read data file
d <- read.csv("data/v6/rawData/OvModel_updatedForNetlogo6 Sensitivity Analysis 10 (Lattice Size)-spreadsheet.csv", 
              header = FALSE, skip = 6)

# transform and clean
d <- 
  d %>%
  gather(key = key, value = value, 2:ncol(d)) %>% 
  spread(key = names(d)[1], value = "value") %>%
  filter(`[steps]` == "10000") %>%
  transmute(Run       = as.numeric(`[run number]`),
            Sens      = as.numeric(`world-width`),
            Strategy  = factor(ifelse(grepl("1", `[initial & final values]`, fixed = TRUE), "Revealers", "Concealers")),
            key       = factor(ifelse(grepl("[cum_paternal_i]", `[initial & final values]`, fixed = TRUE), "PI", "RS")),
            value     = ifelse(V1 == "<RuntimePrimitiveException>", 0, as.numeric(V1))) %>%
  arrange(Run, Strategy) %>%
  fill(Sens) %>%
  spread(key, value)

# save clean file
write.csv(file = "data/v6/cleanData/ovulationSensitivity2_LatticeSize.csv", d, row.names = FALSE)
```

```{r}
d <-
  read.csv('data/v6/cleanData/ovulationSensitivity2_LatticeSize.csv') %>%
  as_tibble() %>%
  mutate(Run       = factor(Run),
         Sens      = factor(Sens),
         Strategy  = factor(Strategy))
```

There are 1000 rows (5 lattice sizes x 100 runs x 2 female strategies).

## 5.1. Analyses

We run mixed ANOVAs to determine (a) the main effect of lattice size, (b) the main effect of Strategy, and (c) the interaction between these. Our first ANOVA includes lifetime reproductive success as the dependent variable.

```{r}
m5.1 <- aov(RS ~ Sens*Strategy + Error(Run/Strategy), data = d)

summary(m5.1)
```

```{r}
model.tables(m5.1, "means")
```

There's a main effect of world size. Presumably, this is because with larger worlds, agents have to spend more time and energy searching for mates. The main effect of Strategy and interaction effect indicate that Concealers have more children than Revealers.

Let's run the same model with paternal investment as the dependent variable.

```{r}
m5.2 <- aov(PI ~ Sens*Strategy + Error(Run/Strategy), data = d)

summary(m5.2)
```

```{r}
model.tables(m5.2, "means")
```

Same pattern.

## 5.2. Visualisation

We now visualise the interaction between lattice size and female strategy with two line graphs, one for each dependent variable. Again, the code for this plot is hidden (see the source .Rmd code for details).

```{r echo=F, warning=F, message=F, fig.height=4, fig.width=12}
d <-
  d %>%
  mutate(Sens = as.numeric(levels(Sens))[Sens])

RS_Summary <- 
  d %>%
  group_by(Sens, Strategy) %>%
  summarise(RS_mean = mean(RS),
            RS_se = sqrt(var(RS) / length(RS)))

p5.1 <- 
  ggplot(d, aes(x = Sens, y = RS, colour = Strategy)) +
    geom_point(aes(y = RS_mean), size = 1, 
               data = RS_Summary, position = position_dodge(width = 0.05), 
               show.legend = FALSE) + 
    geom_errorbar(aes(y = RS_mean, ymin = RS_mean - RS_se, ymax = RS_mean + RS_se), 
                  width = 0.1, position = position_dodge(width = 0.05), data = RS_Summary) +
    geom_line(aes(y = RS_mean), position = position_dodge(width = 0.05), data = RS_Summary) +
    scale_colour_manual(values=c("#ffd3b4", "#6691b1")) +
    xlab("Lattice width (and height)") +
    ylab("Reproductive success\n(number of children)") +
    ylim(c(0,12)) +
    theme_bw() +
    theme(text = element_text(size = 10),
          panel.grid = element_blank()) +
    guides(colour = FALSE)
    

PI_Summary <- 
  d %>%
  group_by(Sens, Strategy) %>%
  summarize(PI_mean = mean(PI),
            PI_se = sqrt(var(PI) / length(PI)))

p5.2 <- 
  ggplot(d, aes(x = Sens, y = PI, colour = Strategy)) +
    geom_point(aes(y = PI_mean), size = 1, 
               data = PI_Summary, position = position_dodge(width = 0.05), show.legend = FALSE) + 
    geom_errorbar(aes(y = PI_mean, ymin = PI_mean - PI_se, ymax = PI_mean + PI_se), 
                  width = 0.1, position = position_dodge(width = 0.05), data = PI_Summary) +
    geom_line(aes(y = PI_mean), position = position_dodge(width = 0.05), data = PI_Summary) +
    scale_colour_manual(values=c("#ffd3b4", "#6691b1")) +
    xlab("Lattice width (and height)") +
    ylab("Paternal investment\n(units)") +
    ylim(c(0,16000)) +
    theme_bw() +
    theme(text = element_text(size = 10),
          panel.grid = element_blank())
    

plot_grid(p5.1, NULL, p5.2, labels = c('a', '', 'b'), nrow = 1, align = 'h',
          rel_widths = c(0.7375, 0.05, 1))

p <- plot_grid(p1.1, NULL, p1.2 + guides(colour = FALSE),
               p2.1, NULL, p2.2 + guides(colour = FALSE),
               p3.1, NULL, p3.2 + guides(colour = FALSE),
               p4.1, NULL, p4.2 + guides(colour = FALSE),
               p5.1, NULL, p5.2 + guides(colour = FALSE),
               labels = c(
                 'a', '', 'b',
                 'c', '', 'd',
                 'e', '', 'f',
                 'g', '', 'h',
                 'i', '', 'j'
                 ), nrow = 5, align = 'h',
               rel_widths = c(1, 0.05, 1))
p <- plot_grid(p, get_legend(p1.2), nrow = 1, rel_widths = c(1, 0.1))

ggsave(p, filename = 'figures/FigureE4.pdf', width = 250, height = 300, units = 'mm')
ggsave(p, filename = 'figures/FigureE4.jpg', width = 250, height = 300, units = 'mm')

# cleanup
rm(PI_Summary, RS_Summary)
```

# 6. Aggression

Finally, we observe the targets of aggression. This isn't a sensitivity analysis as such, just a check to see patterns of aggression over time within the model.

## 6.1. Experiment 2 conditions

We first look at aggression under conditions of Experiment 2 (aggression towards more attractive rivals).

```{r}
d <-
  read.csv('data/v6/cleanData/ovulationAggressTargets_Exp2.csv') %>%
  as_tibble() %>%
  mutate(run       = factor(run),
         target    = factor(target),
         strategy  = factor(strategy))
```

There are 602,439 acts of aggression across all 20 model runs.

Let's see how many acts of aggression there are across model runs. Here, each point is a model run, and the y-axis measures total number of aggression acts.

```{r echo=F, warning=F, error=F, message=F}
d %>%
  group_by(run) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = n, x = "")) +
  geom_boxplot() +
  geom_jitter(width = 0.1) +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks = element_blank()) +
  ylab("Total acts of aggression (count)")
```

There's some variation, but there are around 30,000 acts of aggression per model (on average).

What about over time?

```{r echo=F, warning=F, error=F, message=F}
d %>%
  group_by(run, tick) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  complete(run, tick) %>%
  mutate(n = ifelse(is.na(n), 0, n)) %>%
  ggplot(aes(x = tick, y = n, group = run)) +
  geom_line(stat = "summary_bin", binwidth = 100, fun.y = mean) +
  theme_classic() +
  ylab("Acts of aggression (count)")
```

There are many acts of aggression at the beginning, likely because there is a larger spread of females across the lattice. But when females become pregnant and stay still, the amount of aggression plateaus.

Is there variation in the aggression each individual receives? Each individual is a point in the following plot, split by each independent model run and by the individual's strategy.

```{r echo=F, warning=F, error=F, message=F}
d_summarise <-
  d %>%
  group_by(run, target, strategy) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  complete(run, target) %>%
  fill(strategy) %>%
  mutate(n = ifelse(is.na(n), 0, n))

d_summarise  %>%
  ggplot(aes(x = fct_rev(strategy), y = n, colour = strategy)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(alpha = 0.2, width = 0.1) +
  facet_wrap(.~run) +
  scale_colour_manual(values=c("#ffd3b4", "#6691b1")) +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  xlab("Strategy") +
  ylab("Acts of aggression (count)")
```

What's the average number across simulations for Concealers?

```{r echo=F}
aggress_Concealer <-  
  d_summarise %>%
  filter(strategy == "Concealers") %>%
  pull(n)

mean(aggress_Concealer)
```

And the variation?

```{r echo=F}
sd(aggress_Concealer)
```

Agents receive around 294 acts of aggression on average, with standard deviation 130.

And for Revealers?

```{r echo=F}
aggress_Revealer <-  
  d_summarise %>%
  filter(strategy == "Revealers") %>%
  pull(n)

mean(aggress_Revealer)
```

```{r echo=F}
sd(aggress_Revealer)
```

Does the amount of aggression vary across strategies?

```{r}
summary(lmer(n ~ 1 + strategy + (1 | run), data = d_summarise))
```

Yes. Revealers receive 14 acts of aggression more (on average) than Concealers.

Save histogram to file.

```{r echo=F, warning=F, error=F, message=F}
p6 <-  
  d_summarise %>%
  ggplot(aes(x = n, group = fct_rev(strategy), fill = fct_rev(strategy))) +
  geom_histogram(alpha = 0.5, position = "identity") +
  facet_wrap(.~run) +
  scale_fill_manual(values=c("#6691b1", "#ffd3b4")) +
  theme_classic() +
  theme(legend.title = element_blank(),
        strip.background = element_blank(),
        strip.text = element_blank()) +
  ylab("Frequency") +
  xlab("Acts of aggression received")

p6

ggsave('figures/FigureE7.pdf', width = 200, height = 100, units = 'mm')
ggsave('figures/FigureE7.jpg', width = 200, height = 100, units = 'mm')
```

## 6.2. Experiment 3 conditions

We next look at aggression under conditions of Experiment 3 (aggression towards ovulating rivals).

```{r}
d <-
  read.csv('data/v6/cleanData/ovulationAggressTargets_Exp3.csv') %>%
  as_tibble() %>%
  mutate(run       = factor(run),
         target    = factor(target),
         strategy  = factor(strategy))
```

There are 941,075 acts of aggression across all 20 model runs.

Let's see how many acts of aggression there are across model runs. Here, each point is a model run, and the y-axis measures total number of aggression acts.

```{r echo=F, warning=F, error=F, message=F}
d %>%
  group_by(run) %>%
  summarise(n = n()) %>%
  ggplot(aes(y = n, x = "")) +
  geom_boxplot() +
  geom_jitter(width = 0.1) +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks = element_blank()) +
  ylab("Total acts of aggression (count)")
```

There's some variation in the amount of aggression instantiated across different model runs, but on the whole there are around 47,500 agression acts per simulation. It seems that there's more aggression in Experiment 3 compared to Experiment 2.

What about over time?

```{r echo=F, warning=F, error=F, message=F}
d %>%
  group_by(run, tick) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  complete(run, tick) %>%
  mutate(n = ifelse(is.na(n), 0, n)) %>%
  ggplot(aes(x = tick, y = n, group = run)) +
  geom_line(stat = "summary_bin", binwidth = 100, fun.y = mean) +
  theme_classic() +
  ylab("Acts of aggression (count)")
```

We find the same effect as in Experiment 2.

Is there variation in the amount of aggression each agent receives? Here, each point is an individual agent within a simulation.

```{r echo=F, warning=F, error=F, message=F}
d_summarise <-
  d %>%
  group_by(run, target, strategy) %>%
  summarise(n = n())
  
d_summarise %>%
  ggplot(aes(x = run, y = n)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(alpha = 0.2, width = 0.1) +
  theme_classic() +
  ylab("Acts of aggression (count)")
```

What's the average number across simulations?

```{r echo=F}
mean(d_summarise$n)
```

And the variation?

```{r echo=F}
sd(d_summarise$n)
```

Agents receive around 941 acts of aggression on average, with standard deviation 312.

As a histogram:

```{r echo=F, warning=F, error=F, message=F}
p7 <-  
  d_summarise %>%
  ggplot(aes(x = n, group = strategy, fill = strategy)) +
  geom_histogram() +
  facet_wrap(.~run) +
  scale_fill_manual(values=c("#6691b1", "#ffd3b4")) +
  theme_classic() +
  theme(legend.title = element_blank(),
        strip.background = element_blank(),
        strip.text = element_blank()) +
  ylab("Frequency") +
  xlab("Acts of aggression received")

p7

ggsave('figures/FigureE8.pdf', width = 200, height = 100, units = 'mm')
ggsave('figures/FigureE8.jpg', width = 200, height = 100, units = 'mm')
```

# Session Info

```{r}
sessionInfo()
```