---
title: "The female rivalry hypothesis - Main Experiments"
author: Scott Claessens
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
    toc: true
    number_sections: false
    toc_float: true
---

Load packages.

```{r warning=F, message=F}
library(tidyverse)
library(effsize)
library(gtable)
library(grid)
library(ggplotify)
```

Load data.

```{r}
d <- 
  read.csv('data/ovulationMainExperiments.csv', header=T) %>%
  as_tibble() %>%
  rename(Experiment = `ï..Experiment`) %>%
  mutate(Experiment = factor(Experiment),
         Run        = factor(Run),
         Decrement  = factor(Decrement),
         Strategy   = factor(Strategy))

d
```

Our outcome variables are paternal investment (PI) and lifetime reproductive success (RS). There are 1200 rows in this dataset (3 experiments x 100 model runs x 2 decrement parameters x 2 female strategies).

# Experiment 1 (No Aggression)

## Reproductive Success

Focusing on Experiment 1 first, visualise outcome and check assumptions of normality.

```{r}
d %>%
  filter(Experiment == 1) %>%
  
  ggplot(aes(x = RS)) +
  geom_histogram(bins=30) +
  facet_grid(Decrement ~ Strategy) +
  xlab('Reproductive success (number of children)') +
  theme_minimal()
```

These look approximately normally-distributed. Next, run paired t-tests to look for differences between strategies.

```{r}
RS.dFalse.Revealers  <- d %>% filter(Experiment==1, Decrement=='FALSE', Strategy=='Revealers') %>% pull(RS)
RS.dFalse.Concealers <- d %>% filter(Experiment==1, Decrement=='FALSE', Strategy=='Concealers') %>% pull(RS)
RS.dTrue.Revealers   <- d %>% filter(Experiment==1, Decrement=='TRUE', Strategy=='Revealers') %>% pull(RS)
RS.dTrue.Concealers  <- d %>% filter(Experiment==1, Decrement=='TRUE', Strategy=='Concealers') %>% pull(RS)

t.test(RS.dFalse.Revealers, RS.dFalse.Concealers, paired = TRUE)
```

```{r}
cohen.d(RS.dFalse.Revealers, RS.dFalse.Concealers, paired = TRUE)
```

When Decrement == FALSE, there is a significant difference between the reproductive success of Revealers (Mean = `r round(mean(RS.dFalse.Revealers),2)` children) and Concealers (Mean = `r round(mean(RS.dFalse.Concealers),2)` children), with a small effect size of 0.23.

```{r}
t.test(RS.dTrue.Revealers, RS.dTrue.Concealers, paired = TRUE)
```

```{r}
cohen.d(RS.dTrue.Revealers, RS.dTrue.Concealers, paired = TRUE)
```

When Decrement == TRUE, there is a significant difference between the reproductive success of Revealers (Mean = `r round(mean(RS.dTrue.Revealers),2)` children) and Concealers (Mean = `r round(mean(RS.dTrue.Concealers),2)` children), with a small effect size of -0.21.

## Paternal Investment

Now we check the PI outcome, in Experiment 1.

```{r}
d %>%
  filter(Experiment == 1) %>%
  
  ggplot(aes(x = PI)) +
  geom_histogram(bins=30) +
  facet_grid(Decrement ~ Strategy) +
  xlab('Paternal investment in offspring (units)') +
  theme_minimal()
```

These also look approximately normally-distributed. Run paired t-tests to look for differences between strategies.

```{r}
PI.dFalse.Revealers  <- d %>% filter(Experiment==1, Decrement=='FALSE', Strategy=='Revealers') %>% pull(PI)
PI.dFalse.Concealers <- d %>% filter(Experiment==1, Decrement=='FALSE', Strategy=='Concealers') %>% pull(PI)
PI.dTrue.Revealers   <- d %>% filter(Experiment==1, Decrement=='TRUE', Strategy=='Revealers') %>% pull(PI)
PI.dTrue.Concealers  <- d %>% filter(Experiment==1, Decrement=='TRUE', Strategy=='Concealers') %>% pull(PI)

t.test(PI.dFalse.Revealers, PI.dFalse.Concealers, paired = TRUE)
```

```{r}
cohen.d(PI.dFalse.Revealers, PI.dFalse.Concealers, paired = TRUE)
```

When Decrement == FALSE, there is a significant difference between the paternal investment of Revealers (Mean = `r round(mean(PI.dFalse.Revealers),0)` units) and Concealers (Mean = `r round(mean(PI.dFalse.Concealers),0)` units), with a small effect size of 0.21.

```{r}
t.test(PI.dTrue.Revealers, PI.dTrue.Concealers, paired = TRUE)
```

```{r}
cohen.d(PI.dTrue.Revealers, PI.dTrue.Concealers, paired = TRUE)
```

When Decrement == TRUE, there is no significant difference between the paternal investment of Revealers (Mean = `r round(mean(PI.dTrue.Revealers),0)` units) and Concealers (Mean = `r round(mean(PI.dTrue.Concealers),0)` units), with a negligible effect size of -0.20.

# Experiment 2 (Aggression Towards Higher Mate Value Females)

## Reproductive Success

Now we turn to Experiment 2. For reproductive success, visualise outcome and check assumptions of normality.

```{r}
d %>%
  filter(Experiment == 2) %>%
  
  ggplot(aes(x = RS)) +
  geom_histogram(bins=30) +
  facet_grid(Decrement ~ Strategy) +
  xlab('Reproductive success (number of children)') +
  theme_minimal()
```

As before, these are approximately normally-distributed. Next, run paired t-tests to look for differences between strategies.

```{r}
RS.dFalse.Revealers  <- d %>% filter(Experiment==2, Decrement=='FALSE', Strategy=='Revealers') %>% pull(RS)
RS.dFalse.Concealers <- d %>% filter(Experiment==2, Decrement=='FALSE', Strategy=='Concealers') %>% pull(RS)
RS.dTrue.Revealers   <- d %>% filter(Experiment==2, Decrement=='TRUE', Strategy=='Revealers') %>% pull(RS)
RS.dTrue.Concealers  <- d %>% filter(Experiment==2, Decrement=='TRUE', Strategy=='Concealers') %>% pull(RS)

t.test(RS.dFalse.Revealers, RS.dFalse.Concealers, paired = TRUE)
```

```{r}
cohen.d(RS.dFalse.Revealers, RS.dFalse.Concealers, paired = TRUE)
```

When Decrement == FALSE, there is no significant difference between the reproductive success of Revealers (Mean = `r round(mean(RS.dFalse.Revealers),2)` children) and Concealers (Mean = `r round(mean(RS.dFalse.Concealers),2)` children), with a negligible effect size of -0.18.

```{r}
t.test(RS.dTrue.Revealers, RS.dTrue.Concealers, paired = TRUE)
```

```{r}
cohen.d(RS.dTrue.Revealers, RS.dTrue.Concealers, paired = TRUE)
```

When Decrement == TRUE, there is also no significant difference between the reproductive success of Revealers (Mean = `r round(mean(RS.dTrue.Revealers),2)` children) and Concealers (Mean = `r round(mean(RS.dTrue.Concealers),2)` children), with a negligible effect size of -0.19.

## Paternal Investment

Now we check the PI outcome, in Experiment 2.

```{r}
d %>%
  filter(Experiment == 2) %>%
  
  ggplot(aes(x = PI)) +
  geom_histogram(bins=30) +
  facet_grid(Decrement ~ Strategy) +
  xlab('Paternal investment in offspring (units)') +
  theme_minimal()
```

These also look normally-distributed. Run paired t-tests to look for differences between strategies.

```{r}
PI.dFalse.Revealers  <- d %>% filter(Experiment==2, Decrement=='FALSE', Strategy=='Revealers') %>% pull(PI)
PI.dFalse.Concealers <- d %>% filter(Experiment==2, Decrement=='FALSE', Strategy=='Concealers') %>% pull(PI)
PI.dTrue.Revealers   <- d %>% filter(Experiment==2, Decrement=='TRUE', Strategy=='Revealers') %>% pull(PI)
PI.dTrue.Concealers  <- d %>% filter(Experiment==2, Decrement=='TRUE', Strategy=='Concealers') %>% pull(PI)

t.test(PI.dFalse.Revealers, PI.dFalse.Concealers, paired = TRUE)
```

```{r}
cohen.d(PI.dFalse.Revealers, PI.dFalse.Concealers, paired = TRUE)
```

When Decrement == FALSE, there is no significant difference between the paternal investment of Revealers (Mean = `r round(mean(PI.dFalse.Revealers),0)` units) and Concealers (Mean = `r round(mean(PI.dFalse.Concealers),0)` units), with a negligible effect size of -0.13.

```{r}
t.test(PI.dTrue.Revealers, PI.dTrue.Concealers, paired = TRUE)
```

```{r}
cohen.d(PI.dTrue.Revealers, PI.dTrue.Concealers, paired = TRUE)
```

When Decrement == TRUE, there is also no significant difference between the paternal investment of Revealers (Mean = `r round(mean(PI.dTrue.Revealers),0)` units) and Concealers (Mean = `r round(mean(PI.dTrue.Concealers),0)` units), with a negligible effect size of -0.13.

# Experiment 3 (Aggression Towards Ovulating Females)

## Reproductive Success

Finally, we turn to Experiment 3. For reproductive success, visualise outcome and check assumptions of normality.

```{r}
d %>%
  filter(Experiment == 3) %>%
  
  ggplot(aes(x = RS)) +
  geom_histogram(bins=30) +
  facet_grid(Decrement ~ Strategy) +
  xlab('Reproductive success (number of children)') +
  theme_minimal()
```

As before, these appear normally-distributed. Next, run paired t-tests.

```{r}
RS.dFalse.Revealers  <- d %>% filter(Experiment==3, Decrement=='FALSE', Strategy=='Revealers') %>% pull(RS)
RS.dFalse.Concealers <- d %>% filter(Experiment==3, Decrement=='FALSE', Strategy=='Concealers') %>% pull(RS)
RS.dTrue.Revealers   <- d %>% filter(Experiment==3, Decrement=='TRUE', Strategy=='Revealers') %>% pull(RS)
RS.dTrue.Concealers  <- d %>% filter(Experiment==3, Decrement=='TRUE', Strategy=='Concealers') %>% pull(RS)

t.test(RS.dFalse.Revealers, RS.dFalse.Concealers, paired = TRUE)
```

```{r}
cohen.d(RS.dFalse.Revealers, RS.dFalse.Concealers, paired = TRUE)
```

When Decrement == FALSE, there is a significant difference between the reproductive success of Revealers (Mean = `r round(mean(RS.dFalse.Revealers),2)` children) and Concealers (Mean = `r round(mean(RS.dFalse.Concealers),2)` children), with a large effect size of -2.72.

```{r}
t.test(RS.dTrue.Revealers, RS.dTrue.Concealers, paired = TRUE)
```

```{r}
cohen.d(RS.dTrue.Revealers, RS.dTrue.Concealers, paired = TRUE)
```

When Decrement == TRUE, there is again a significant difference between the reproductive success of Revealers (Mean = `r round(mean(RS.dTrue.Revealers),2)` children) and Concealers (Mean = `r round(mean(RS.dTrue.Concealers),2)` children), with a large effect size of -3.25.

## Paternal Investment

Now we check the PI outcome, in Experiment 3.

```{r}
d %>%
  filter(Experiment == 3) %>%
  
  ggplot(aes(x = PI)) +
  geom_histogram(bins=30) +
  facet_grid(Decrement ~ Strategy) +
  xlab('Paternal investment in offspring (units)') +
  theme_minimal()
```

These also look normally-distributed. Run paired t-tests to look for differences between strategies.

```{r}
PI.dFalse.Revealers  <- d %>% filter(Experiment==3, Decrement=='FALSE', Strategy=='Revealers') %>% pull(PI)
PI.dFalse.Concealers <- d %>% filter(Experiment==3, Decrement=='FALSE', Strategy=='Concealers') %>% pull(PI)
PI.dTrue.Revealers   <- d %>% filter(Experiment==3, Decrement=='TRUE', Strategy=='Revealers') %>% pull(PI)
PI.dTrue.Concealers  <- d %>% filter(Experiment==3, Decrement=='TRUE', Strategy=='Concealers') %>% pull(PI)

t.test(PI.dFalse.Revealers, PI.dFalse.Concealers, paired = TRUE)
```

```{r}
cohen.d(PI.dFalse.Revealers, PI.dFalse.Concealers, paired = TRUE)
```

When Decrement == FALSE, there is a significant difference between the paternal investment of Revealers (Mean = `r round(mean(PI.dFalse.Revealers),0)` units) and Concealers (Mean = `r round(mean(PI.dFalse.Concealers),0)` units), with a large effect size of -2.72.

```{r}
t.test(PI.dTrue.Revealers, PI.dTrue.Concealers, paired = TRUE)
```

```{r}
cohen.d(PI.dTrue.Revealers, PI.dTrue.Concealers, paired = TRUE)
```

When Decrement == TRUE, there is a significant difference between the paternal investment of Revealers (Mean = `r round(mean(PI.dTrue.Revealers),0)` units) and Concealers (Mean = `r round(mean(PI.dTrue.Concealers),0)` units), with a large effect size of -3.54.

# Plotting the results of the main experiments

We create violin plot summarising our outcomes for both Concealers and Revealers, when decrement is both True and False, in all three Experiments. The code is hidden here (see the source .Rmd file), but this is the result for reproductive success:

```{r echo=F, warning=F, message=F}
RS_Summary <- 
  d %>%
  mutate(Strategy   = fct_relevel(Strategy, c('Revealers', 'Concealers')),
         Experiment = factor(paste('Experiment ', Experiment)),
         Decrement  = factor(ifelse(Decrement == 'TRUE', 'Decrement = TRUE', 'Decrement = FALSE'))) %>%
  group_by(Experiment, Decrement, Strategy) %>%
  summarise(RS_mean = mean(RS),
            RS_se   = sd(RS) / sqrt(length(RS)))

p1 <- 
  d %>%
  mutate(Strategy   = fct_relevel(Strategy, c('Revealers', 'Concealers')),
         Experiment = factor(paste('Experiment ', Experiment)),
         Decrement  = factor(ifelse(Decrement == 'TRUE', 'Decrement = TRUE', 'Decrement = FALSE'))) %>%

  ggplot(aes(x = Strategy, y = RS, fill = Strategy)) +
  geom_violin(stat = "ydensity") +
  geom_jitter(colour = "black", size = 0.6, width = 0.13, alpha = 0.04, show.legend = FALSE) +
  geom_point(data = RS_Summary, aes(y = RS_mean), color = "black", size = 0.6, show.legend = FALSE) + 
  geom_errorbar(data = RS_Summary, aes(y = RS_mean, ymin = RS_mean-RS_se, ymax = RS_mean+RS_se),
                color = "black", width = 0.3) +
  facet_grid(. ~ Experiment + Decrement) +
  ylab('Lifetime reproductive success\n(number of children)') +
  scale_fill_manual(values=c("#6691b1", "#ffd3b4")) +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x  = element_blank(),
        axis.title.y = element_text(margin = margin(r = 10)),
        legend.title = element_blank(),
        legend.text  = element_text(margin = margin(r = 10, l = 2)),
        legend.position = 'bottom',
        legend.margin = margin(0,0,0,0),
        panel.grid.minor = element_blank(),
        text = element_text(size = 7))

# extend width between experiments
pgt <- ggplot_gtable(ggplot_build(p1))
pgt$widths[8] <- pgt$widths[12] <- pgt$widths[8]*4
p1 <- as.ggplot(pgt)

# manually add new facet labels
p1 <- 
  p1 + 
  annotate('rect', xmin = 0, xmax= 1, ymin = 0.93, ymax = 1, fill = 'white') +
  annotate('text', x = 0.213, y = 0.965, 
           label = 'Experiment 1\n(No Aggression)', size = 2) +
  annotate('text', x = 0.532, y = 0.965, 
           label = 'Experiment 2\n(Aggression Towards Higher Attractiveness)', size = 2) +
  annotate('text', x = 0.851, y = 0.965, 
           label = 'Experiment 3\n(Aggression Towards Ovulating)', size = 2)
  
ggsave('figures/Figure1.pdf', plot = p1, width = 180, height = 90, units = 'mm')
ggsave('figures/Figure1.png', plot = p1, width = 180, height = 90, units = 'mm')

p1
```

And the plot for paternal investment:

```{r echo=F, warning=F, message=F}
PI_Summary <- 
  d %>%
  mutate(Strategy   = fct_relevel(Strategy, c('Revealers', 'Concealers')),
         Experiment = factor(paste('Experiment ', Experiment)),
         Decrement  = factor(ifelse(Decrement == 'TRUE', 'Decrement = TRUE', 'Decrement = FALSE'))) %>%
  group_by(Experiment, Decrement, Strategy) %>%
  summarise(PI_mean = mean(PI),
            PI_se   = sd(PI) / sqrt(length(PI)))

p2 <- 
  d %>%
  mutate(Strategy   = fct_relevel(Strategy, c('Revealers', 'Concealers')),
         Experiment = factor(paste('Experiment ', Experiment)),
         Decrement  = factor(ifelse(Decrement == 'TRUE', 'Decrement = TRUE', 'Decrement = FALSE'))) %>%

  ggplot(aes(x = Strategy, y = PI, fill = Strategy)) +
  geom_violin(stat = "ydensity") +
  geom_jitter(colour = "black", size = 0.6, width = 0.13, alpha = 0.04, show.legend = FALSE) +
  geom_point(data = PI_Summary, aes(y = PI_mean), color = "black", size = 0.6, show.legend = FALSE) + 
  geom_errorbar(data = PI_Summary, aes(y = PI_mean, ymin = PI_mean-PI_se, ymax = PI_mean+PI_se),
                color = "black", width = 0.3) +
  facet_grid(. ~ Experiment + Decrement) +
  ylab('Paternal investment (units)') +
  scale_fill_manual(values=c("#6691b1", "#ffd3b4")) +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x  = element_blank(),
        axis.title.y = element_text(margin = margin(r = 10)),
        legend.title = element_blank(),
        legend.text  = element_text(margin = margin(r = 10, l = 2)),
        legend.position = 'bottom',
        legend.margin = margin(0,0,0,0),
        panel.grid.minor = element_blank(),
        text = element_text(size = 7))

# extend width between experiments
pgt <- ggplot_gtable(ggplot_build(p2))
pgt$widths[8] <- pgt$widths[12] <- pgt$widths[8]*4
p2 <- as.ggplot(pgt)

# manually add new facet labels
p2 <- 
  p2 + 
  annotate('rect', xmin = 0, xmax= 1, ymin = 0.93, ymax = 1, fill = 'white') +
  annotate('text', x = 0.213, y = 0.965, 
           label = 'Experiment 1\n(No Aggression)', size = 2) +
  annotate('text', x = 0.532, y = 0.965, 
           label = 'Experiment 2\n(Aggression Towards Higher Attractiveness)', size = 2) +
  annotate('text', x = 0.851, y = 0.965, 
           label = 'Experiment 3\n(Aggression Towards Ovulating)', size = 2)
  
ggsave('figures/FigureS1.pdf', plot = p2, width = 180, height = 90, units = 'mm')
ggsave('figures/FigureS1.png', plot = p2, width = 180, height = 90, units = 'mm')

p2
```

# Session Info

```{r}
sessionInfo()
```

